Lecture Notes in Computer Science:\\Authors' Instructions for the Preparation\\of Camera-Ready Contributions\\to LNCS/LNAI/LNBI Proceedings

### 2013-04-25 papers/sle2013/sle2013.tex
sle directory

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\usepackage{url}
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\input{macros}

@@

\title{JavaScript as an embedded DSL in Scala}
% a short form should be given in case it is too long for the running head
%\titlerunning{}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Grzegorz Kossakowski \and Nada Amin \and Tiark Rompf \and Martin Odersky}
%
\authorrunning{JavaScript as an embedded DSL in Scala}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Ecole Polytechnique F\'ed\'erale de Lausanne,\\
\email{\{first.last\}@epfl.ch}}
%\mailsa\\
%\mailsb\\
%\url{http://lamp.epfl.ch}}

@@

%\toctitle{}
%\tocauthor{}
\maketitle

\begin{abstract}
% =>70 & <=150 words
\note{TODO}

\keywords{JavaScript, Scala, DSL, programming languages}
\end{abstract}

We use Lightweight Modular Staging (LMS) to create a DSL in Scala which generates JavaScript code.

Our approach addresses many problems encountered in web development in an elegant, coherent and lightweight way. Programming directly in JavaScript include the following problems:
\begin{itemize}
\item lack of static typing, which makes it difficult to maintain, refactor and develop large web applications,
\item impedance mismatch between client and server code,
\item lack of modularity and abstractions,
\item difficult to reason about control structures that arise from high-performance asynchronous callback-driven programming style.
\end{itemize}
Frameworks such as GWT and Links which generates JavaScript solve some of the issues, but introduce new problems, including:
\begin{itemize}
\item lack of integration with existing JavaScript libraries,
\item difficult to extend with new APIs, let alone new language primitives,
\item little control over generated code which makes performance-tuning very difficult,
\item no first-class status for generated code, which makes it impossible to compose and abstract over snippets.
\end{itemize}

Our approach is lightweight: By embedding our DSL as a library in Scala, we exploit the features of the host language such as expressive static typing, easy creation of new control structures, and even partial CPS transformation.

\section{Introduction to LMS}
- virtualization
- rep types
- IR construction
- code generation
advantage: can have abstractions that only exist at staging-time

\section{Gradual Typing}
- Scala Dynamic
- use of external APIs
- snippets with a simple example showing evolution from dynamic to typed (Canvas example which will become Koch example in the next section)

\section{Trivial Embedding}
- DOM Canvas Koch example: generate both client-side code or desktop widget

\section{Modularity Interlude}
- modularity at many levels
   e.g. dynamic feature is just a trait
   users specify external APIs with traits
   interpretation of rep also done via traits (generating IR nodes vs trivial embedding)
- example of user adding a language primitive: e.g. for-comprehension
- mix and match features by composing traits (e.g. everything available on main thread 'JS trait', vs no-DOM manipualtion in worker threads 'WorkerJS trait)

\section{Reification of Objects}
- JS Literals: intuitive translation to JS as useful JSON-like objects, static typing
- mice example: shows use of JSLiterals + API gluing (create abstractions that you need, not necessarily exactly matching the underlying JS API)
- reification of traits: mutability, inheritance

\section{Case Study: CPS transformation to simply asynchronous web development}

\clearpage
\section{Introduction}

@@

If screenshots are necessary, please make sure that you are happy with
the print quality before you send the files.
\begin{figure}
\centering
%\includegraphics[height=6.2cm]{eijkel2}
\caption{One kernel at $x_s$ (\emph{dotted kernel}) or two kernels at
$x_i$ and $x_j$ (\textit{left and right}) lead to the same summed estimate
at $x_s$. This shows a figure consisting of different types of
lines. Elements of the figure described in the caption should be set in
italics, in parentheses, as shown in this sample caption.}
\label{fig:example}
\end{figure}

>>>>

@@

\usepackage{url}
\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% first the title is needed
\title{Lecture Notes in Computer Science:\\Authors' Instructions
for the Preparation\\of Camera-Ready
Contributions\\to LNCS/LNAI/LNBI Proceedings}

% a short form should be given in case it is too long for the running head
\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Alfred Hofmann%
\thanks{Please note that the LNCS Editorial assumes that all authors have used
the western naming convention, with given names preceding surnames. This determines
the structure of the names in the running heads and the author index.}%
\and Ursula Barth\and Ingrid Haas\and Frank Holzwarth\and\\
Anna Kramer\and Leonie Kunz\and Christine Rei\ss\and\\
Nicole Sator\and Erika Siebert-Cole\and Peter Stra\ss er}
%
\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Springer-Verlag, Computer Science Editorial,\\
Tiergartenstr. 17, 69121 Heidelberg, Germany\\
\mailsa\\
\mailsb\\
\mailsc\\
\url{http://www.springer.com/lncs}}

@@

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}
\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper and should
contain at least 70 and at most 150 words. It should be written using the
\emph{abstract} environment.
\keywords{We would like to encourage you to list your keywords within
the abstract section}
\end{abstract}

\section{Introduction}

@@

If screenshots are necessary, please make sure that you are happy with
the print quality before you send the files.
\begin{figure}
\centering
\includegraphics[height=6.2cm]{eijkel2}
\caption{One kernel at $x_s$ (\emph{dotted kernel}) or two kernels at
$x_i$ and $x_j$ (\textit{left and right}) lead to the same summed estimate
at $x_s$. This shows a figure consisting of different types of
lines. Elements of the figure described in the caption should be set in
italics, in parentheses, as shown in this sample caption.}
\label{fig:example}
\end{figure}
